---
title: "Lab4Package"
author: "Hussnain Khalid and Carl Ryttmarker"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab4Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab4Package)
```
# Usage

In this package we attempt to construct the <Linear Regression> package.

Linear regression function:
```{r}
data("iris")
# linear = linreg(Petal.Length ~ Species + Sepal.Width, data = iris)
linear = linreg(Petal.Length~Sepal.Width+Sepal.Length, data = iris)
```
For a quick overview of our model we print out the coefficients and coefficient names, similar as done by the Linear Regression package.

```{r}
print(linear)
```
Plot of "Residuals vs Fitted" graph and the "Scale-Location" graph:

```{r fig, fig.height = 5, fig.width = 5, fig.align = "center"}
linear1 = linreg(Petal.Length~Species, data = iris)
plot(linear1)
```

For vector of residuals, similar as done by the Linear Regression package.

```{r}
resid(linear)
```

For predicted values, similar as done by the Linear Regression package.

```{r}
pred(linear)
```

For coefficients, similar as done by the Linear Regression package.

```{r}
coef(linear)
```
For summary, similar as done by the Linear Regression package.

```{r}
summary(linear)
```
